### 2016-10-05 robust-software.tex
Testing installation using Docker

\item
When we tell people not to require root privileges,
we should point out that testing in a virtual machine is a good way to check for this.

@@

>>>>

@@

Note:
testing software installation has traditionally been regarded as difficult,
since it necessarily alters the machine on which the test is conducted.
Lightweight virtualization containers like Docker make this much easier as well.
